Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-21 paper.qmd
Replot Figure 15

```{r}
# label: read-pbmc-nldr
# Read a variety of different NLDR representations of PBMC
# and plot them on same aspect ratio
clr_choice <- "#0077A3"
umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_30_min_dist_0.3.rds")

@@

@@

@@

@@

@@

@@

@@

pacmap_pbmc <- read_rds("data/pbmc3k/pbmc_pacmap_30_random_0.9_5.rds")
nldr8 <- pacmap_pbmc |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("h")
```

@@

```{r}
#| fig-cap: "MSE from UMAP with diffferent (hyper-)parameter choices and tSNE with default (hyper-)parameter setting applied to PBMC3k dataset for different number of bins along the x-axis ($b_1$). Which is the most reasonable representation of the structures present in the PBMC3k data? The residual plot have a steep slope at the beginning, indicating that a smaller $b_1$ causes a larger amount of error. Then, the slope gradually declines or level off, indicating that a higher number of $b_1$ generates a smaller error. It was observed that for every $b_1$, the lowest error occurred with tSNE using the perplexity: $30$."
#| label: fig-pbmc-mse
#| fig-pos: H
#| out-width: 70%

error_plot_pbmc
```

>>>>

```{r}
#| label: read-pbmc-nldr
# Read a variety of different NLDR representations of PBMC
# and plot them on same aspect ratio
clr_choice <- "#0077A3"
umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_30_min_dist_0.3.rds")

@@

nldr1c <- umap_pbmc |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("a")

@@

nldr2c <- umap_pbmc |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1, colour='#f781bf') +
  interior_annotation("b")

@@

nldr3c <- umap_pbmc |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1, colour='#999999') +
  interior_annotation("c")

@@

nldr4c <- tsne_pbmc |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#984ea3') +
  interior_annotation("d")

@@

nldr5c <- tsne_pbmc |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  interior_annotation("e")

@@

nldr6c <- phate_pbmc |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1, colour='#377eb8') +
  interior_annotation("f")

@@

nldr7c <- trimap_pbmc |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  interior_annotation("g")

pacmap_pbmc <- read_rds("data/pbmc3k/pbmc_pacmap_30_random_0.9_5.rds")
nldr8 <- pacmap_pbmc |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("h")

nldr8c <- pacmap_pbmc |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("h")
```

@@

```{r}
#| fig-cap: "MSE from UMAP with diffferent (hyper-)parameter choices and tSNE with default (hyper-)parameter setting applied to PBMC3k dataset for different number of bins along the x-axis ($b_1$). Which is the most reasonable representation of the structures present in the PBMC3k data? The residual plot have a steep slope at the beginning, indicating that a smaller $b_1$ causes a larger amount of error. Then, the slope gradually declines or level off, indicating that a higher number of $b_1$ generates a smaller error. It was observed that for every $b_1$, the lowest error occurred with tSNE using the perplexity: $30$."
#| label: fig-pbmc-mse
#| fig-pos: H
#| out-height: 100%

free(error_plot_pbmc) / wrap_plots(nldr1c, nldr2c, nldr3c, nldr4c,
           nldr5c, nldr6c, nldr7c, nldr8c, ncol = 4)
```
